---
title: "country report"
output: html_document
params:
  df: ""
  selected_country: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```


```{r }
source("../functions.R")

df <- params$df
selected_country <- params$selected_country

tbl <- summary_all_func(df %>% filter(`Country / Territory` == selected_country))
# table <- summary_country_func(tbl = summary_all_func(df), selected_country = selected_country)
common_attacks <- common_attack_types_func(tbl = df, selected_country = selected_country) %>% head(5)

```

```{r}
n_attacks <- sum(tbl$total_attacks)
n_casualties <- sum(tbl$total_casualties)
n_injured <- sum(tbl$total_injured)
n_death <- sum(tbl$total_death)
n_hw <- sum(tbl$`hw_abduction/arrest/detention`)
n_patient <- sum(tbl$`patient_abduction/arrest/detention`)
n_casualty_death_ratio <- n_casualties / n_attacks

```


### Casualties to attacks ratio: `r round(n_casualty_death_ratio, 2)`:1

Overall, **`r n_attacks`** attacks have been reported on healthcare facilities in `r selected_country`.
The number of reported casualties is **`r n_casualties`** (injuries = `r n_injured`, deaths = `r n_death`).

Moreover, **`r n_hw`** health workers and **`r n_patient`** patients have been abducted, arrested, or detained.

Common attack types that occurred in `r selected_country` are:

```{r results='asis'}
cat("<ul>")

for (i in 1:nrow(common_attacks)) {
  result <- glue::glue("<li>{common_attacks[i,]$attack_type}: {common_attacks[i,]$Freq}</li>")
  cat(result)
}
  
cat("</ul>")
```




